MSAD-PCA Walkthrough

### 2023-06-29 LaTeX_Vignette/MS-MVSPC_DissertationVignette.Rnw
Spell checking

We outline this vignette as follows. In Section \ref{sec:D_Motivation}, we discuss the motivation for creating this package, and briefly explain the utility of multi-state process monitoring. In Section \ref{sec:D_DataGen}, we offer a thorough explination of how to generate the synthetic data we employed to test and compare the new multi-state modification of the process monitoring setup with the \texttt{mspProcessData} function. In Section \ref{sec:D_Train}, we describe the necessary information and data formatting to effectively train the fault detection algorithm using the \texttt{mspTrain} function. Then, in Section \ref{sec:D_Alarms}, we list and explain the necessary inputs to the \texttt{mspMonitor} and \texttt{mspWarning} functions and examine their outputs. Section \ref{sec:D_Workflow} shows a step-by-step walkthrough of how to implement the four \texttt{mvMonitoring} functions in practice. We offer some concluding remarks in Section \ref{sec:D_Conclusion}.

@@

The \texttt{xts} object class stands for \emph{extendible time series} and comes from the package \texttt{xts}, which is built on the package \texttt{zoo}. The date and time information for the multivariate stochastic process (necessarily as \texttt{POSIX} objects) are stored as the row indices of \texttt{xts} matrices. We recommend the package \texttt{lubridate} for manipulating \texttt{POSIX} objects.

>>>>

We outline this vignette as follows. In Section \ref{sec:D_Motivation}, we discuss the motivation for creating this package, and briefly explain the utility of multi-state process monitoring. In Section \ref{sec:D_DataGen}, we offer a thorough explanation of how to generate the synthetic data we employed to test and compare the new multi-state modification of the process monitoring setup with the \texttt{mspProcessData} function. In Section \ref{sec:D_Train}, we describe the necessary information and data formatting to effectively train the fault detection algorithm using the \texttt{mspTrain} function. Then, in Section \ref{sec:D_Alarms}, we list and explain the necessary inputs to the \texttt{mspMonitor} and \texttt{mspWarning} functions and examine their outputs. Section \ref{sec:D_Workflow} shows a step-by-step walkthrough of how to implement the four \texttt{mvMonitoring} functions in practice. We offer some concluding remarks in Section \ref{sec:D_Conclusion}.

@@

The \texttt{xts} object class stands for \emph{extendable time series} and comes from the package \texttt{xts}, which is built on the package \texttt{zoo}. The date and time information for the multivariate stochastic process (necessarily as \texttt{POSIX} objects) are stored as the row indices of \texttt{xts} matrices. We recommend the package \texttt{lubridate} for manipulating \texttt{POSIX} objects.

### 2023-06-29 inst/Simulation_Vignette.Rmd
Spell checking

###  Features and State Features
We will simulate three features, with each feaure operating under $k$ different states. We will use $<x(t), y(t), z(t)>$ instead of the $<x_1(t), x_2(t), x_3(t)>$ notation used in Kazor et al. This will assist us when we introduce feature states. Our state notation will be $<x_k(t), y_k(t), z_k(t)>$ for State $k$.

@@

Now we clean up the environment, and load the data we've saved.
```{r sweepEnv}
# # uncomment these lines to use the data from the package. Comment them out
# # when generating new data.
# rm(list = ls())
# load("~/Documents/GitHub/mvMonitoring/data/normal_switch_xts.rda")
# load("~/Documents/GitHub/mvMonitoring/data/fault1A_xts.rda")
# load("~/Documents/GitHub/mvMonitoring/data/fault1B_xts.rda")
# load("~/Documents/GitHub/mvMonitoring/data/fault2A_xts.rda")
# load("~/Documents/GitHub/mvMonitoring/data/fault2B_xts.rda")
# load("~/Documents/GitHub/mvMonitoring/data/fault3A_xts.rda")
# load("~/Documents/GitHub/mvMonitoring/data/fault3B_xts.rda")

@@

# False Alarms? 
alarmData[,15] %>% sum(na.rm = T)
alarmData[,11:15] %>% head
alarmData[,11:15] %>% tail

@@

### Import the Data files
First, we import the two data sets. 
```{r realData_import}
library(readr)
if(.Platform$OS.type == "windows"){
  tenDayData_v2 <- read_csv("~/GitHub/mvMonitoring/mvMonitoring/inst/tenDayData_v2.csv", 
  col_types = cols(X1 = col_datetime(format = "%Y-%m-%d %H:%M:%S")))
currentDayData_v2 <- read_csv("~/GitHub/mvMonitoring/mvMonitoring/inst/currentDayData_v2.csv", 
  col_types = cols(X1 = col_datetime(format = "%Y-%m-%d %H:%M:%S")))
}else{
  tenDayData_v2 <- read_csv("~/Documents/GitHub/mvMonitoring/inst/tenDayData_v2.csv", 
                col_types = cols(X1 = col_datetime(format = "%Y-%m-%d %H:%M:%S")))
currentDayData_v2 <- read_csv("~/Documents/GitHub/mvMonitoring/inst/currentDayData_v2.csv",
                col_types = cols(X1 = col_datetime(format = "%Y-%m-%d %H:%M:%S")))
}

@@

### Training the AD-PCA Model
Now to analyse the training data, and pass the training information in order to test the testing data. Because the data do not come from a process with recorded state variables (or, more specifically, that we do not have such state information), we will give a column of 1s as the labels. Futher, we have ten days' worth of 10-minute-level observations, so we will train on $7 * 24 * 60 / 10 = 1008$ observations (seven days' worth), and update each day ($24 * 60 * 10 = 144$). Further, we will lag the features by one time step. CAVEAT: we're missing one observation: the `tenDay_clean` data matrix had 1299 rows, while our train (864) and returned faultChecks (434) account for 1298 rows. This missing row is the row we lost due to the lag.
```{r trainRealData}
tenDayResults_ls <- mvMonitoring::mspTrain(data = tenDay_clean,
                         labelVector = rep(1, nrow(tenDay_clean)),
                         trainObs = 1008,
                         updateFreq = 144,
                         alpha = 0.001,
                         faultsToTriggerAlarm = 3,
                         lagsIncluded = 0:1,
                         var.amnt = 0.95)
```

@@

realDataandFlags <- mvMonitoring::mspMonitor(observations = laggedOneDay,
           labelVector = rep(1, nrow(laggedOneDay)),
           trainingSummary = tenDayResults_ls$TrainingSpecs)
realDataandFlags[1,]
```
For some reason, that I don't know right now, `mspMonitor` is flagging all of these values as faults, which will trigger alarms for most of the day.
```{r realWarnings}
# These lines will test each line as if it was just received:
realAlarmData <- realDataandFlags
for(i in 1:nrow(realDataandFlags)){
  realAlarmData[1:i,] <- mvMonitoring::mspWarning(realAlarmData[1:i,])
}
tail(realAlarmData)
```
I'm not sure why this is happening. I'll have to dig in to it later. I do notice that both the SPE and T2 statistics are off the charts. The only component affecting them equally is the projection matrix P. We are estimating a 70 ^ 2 matrix using only 432 observations at a time, so this matrix could very well be unstable (we'd need around 2500 observations to stably estimate the scatter matrix).
EDIT: I was not supplying the training mean vector and precision matrix to the monitoring function, which means that the the test observations were not being centred and scaled. This did not make much impact in the simulated data, as the centered and scaled data would not be far off from the original values, except in state 2. This issue is fixed.

# Simulation Setup
We have also collapsed the data generation setup and implementation from this vignette into a function suite. The outward-facing function is called `mspProcessData`, and we now give an example.
```{r mspProcessEg}
simFaults_ls <- mspProcessData(faults = "All",
                               faultStartIndex = 8500,
                               startTime = "2016-11-27 00:00:00 CST")

@@

## True Multi-State Observations
We first assume that the observations do come from a multi-state process. This means that we will test AD-PCA by incorrectly assuming that all observations come from the same state. We first draw a list of data matrices. Then we look at false alarm rates for multi-state data under normal operating conditions using AD-PCA and MSAD-PCA. We also measure detection time for all faults for multi-state data under normal operating conditions using AD-PCA and MSAD-PCA.
```{r trueMultiState_sim, message = FALSE}
# We get warnings of "no non-missing arguments to min; returning Inf" when
# none of the observations yield alarms. Suppress this with ? "message = FALSE"
# doesn't work.
library(parallel) # use mclapply on Mac, parLapply on Windows
library(tidyverse)
library(xts)
a <- Sys.time()
cl <- makeCluster(getOption("cl.cores", 8))
clusterEvalQ(cl, library(tidyverse))
clusterEvalQ(cl, library(xts))
clusterEvalQ(cl, library(mvMonitoring))
msadResults5_ls <- parLapply(cl = cl, 1:100, function(void){
# msadResults2_ls <- mclapply(1:1000, mc.cores = 8L, function(void){

  ##########   Draw a Random Data Set   ##########
  msadpcaObs_ls <- mspProcessData(faults = c("NOC", "C1", "C2", "C3"), # "All"
                              faultStartIndex = 8500,
                              startTime = "2016-11-27 00:00:00 CST",
                              multiState = TRUE,
                              adpcaTest = TRUE)

@@

  # Subset out the normal operating data
  faultsSimRes <- lapply(msadpcaObs_ls[names(msadpcaObs_ls) != "NOC"],
                         function(mat){
    # Testing the apply statement
    # mat <- msadpcaObs_ls$C1

@@

    ## Time to first alarm
    # Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
    # Use suppressWarnings() on the min() function. If the which() function
    # returns an integer(0), its minimum is Inf, but it throws a warning. These
    # warnings will fill the console under heavy repitition, so suppress them.
    # SPE
    # All alarms: which(msad_MS_Alarm[1:2580,15] %in% c(2,3))
    time2SPE_msad <- which(msad_MS_Alarm[1000:2580,15] %in% c(2,3))
    time2SPE_msad <- suppressWarnings(min(time2SPE_msad))
    # T2
    # All alarms: which(msad_MS_Alarm[1:2580,15] %in% c(1,3))
    time2T2_msad <- which(msad_MS_Alarm[1000:2580,15] %in% c(1,3))
    time2T2_msad <- suppressWarnings(min(time2T2_msad))

@@

    ## Time to first alarm
    # Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
    # SPE
    # All alarms: which(ad_MS_Alarm[,15] %in% c(2,3))
    time2SPE_ad <- which(ad_MS_Alarm[1000:2580,15] %in% c(2,3))
    time2SPE_ad <- suppressWarnings(min(time2SPE_ad))
    # T2
    # All alarms: which(ad_MS_Alarm[,15] %in% c(1,3))
    time2T2_ad <- which(ad_MS_Alarm[1000:2580,15] %in% c(1,3))
    time2T2_ad <- suppressWarnings(min(time2T2_ad))

@@

  ##########   Return a List   ##########
  list(falseAlarmRates = FA_rates,
       time2Detect = faultsSimRes)
})
b <- Sys.time() 
b - a # 91 seconds for each iteration. 15.3 minutes for 10 iterations, 12.1 
# hours for 500 iterations. On parallel Mac, 5.3 minutes for 10 iterations over
# 8 cores, 41.4 minutes for 100 iterations over 8 cores, and 6.7 hours for 1000
# iterations over 8 cores. On parallel Windows, 4.3 minutes for 10 iterations
# over 8 cores, and 5.4 hours for 1000 iterations over 8 cores.
stopCluster(cl)
```
Let's clean up these results.
```{r msadSim_Cleaning}
ms_FA_rates5 <- lapply(1:length(msadResults5_ls), function(i){
  msadResults5_ls[[i]]$falseAlarmRates
}) %>% do.call(bind_rows, .)
write_csv(ms_FA_rates4, path = "false_alarm_rates_ms_1000_20170323.csv")
ms_detectionTimes5 <- lapply(1:length(msadResults5_ls), function(i){
  msadResults5_ls[[i]]$time2Detect
}) %>% do.call(bind_rows, .)
write_csv(ms_detectionTimes4, path = "detection_times_ms_1000_20170323.csv")
```

Now we can look at the results.
```{r msadSim_graphics}
# False Alarm Rates
ms_FA_rates3[,1] %>% hist(xlim = c(0, 0.05), main = "MSAD SPE False Alarm Rates")
ms_FA_rates3[,2] %>% hist(xlim = c(0, 0.05), main = "MSAD T2 False Alarm Rates")
ms_FA_rates3[,3] %>% hist(xlim = c(0, 0.05), main = "AD SPE False Alarm Rates")
ms_FA_rates3[,4] %>% hist(xlim = c(0, 0.05), main = "AD T2 False Alarm Rates")

###  Detection Times  ###
# Fault 1A
ms_detectionTimes3 %>%
  filter(Faults == "A1") %>%
  select(-Faults) %>% 
  sapply(summary)

# Fault 1B
ms_detectionTimes3 %>%
  filter(Faults == "B1") %>%
  select(-Faults) %>% 
  sapply(summary)

# Fault 2A
ms_detectionTimes3 %>%
  filter(Faults == "A2") %>%
  select(-Faults) %>% 
  sapply(summary)

# Fault 2B
ms_detectionTimes3 %>%
  filter(Faults == "B2") %>%
  select(-Faults) %>% 
  sapply(summary)

# Fault 3A
ms_detectionTimes3 %>%
  filter(Faults == "A3") %>%
  select(-Faults) %>% 
  sapply(summary)

# Fault 3B
ms_detectionTimes3 %>%
  filter(Faults == "B3") %>%
  select(-Faults) %>% 
  sapply(summary)

@@

## True Single-State Observations
We first assume that the observations do not come from a multi-state process. This means that we will test MSAD-PCA by incorrectly assuming that observations come from different states: we will assign a state at random to each observation from "1", "2", or "3". We first draw a list of data matrices. Then we look at false alarm rates for multi-state data under normal operating conditions using AD-PCA and MSAD-PCA. We also measure detection time for all faults for single-state data under normal operating conditions using AD-PCA and MSAD-PCA.
```{r trueSingleState_sim, message = FALSE}
library(parallel) # use mclapply on Mac, parLapply on Windows
library(tidyverse)
library(xts)
a <- Sys.time()
cl <- makeCluster(getOption("cl.cores", 8))
clusterEvalQ(cl, library(tidyverse))
clusterEvalQ(cl, library(xts))
clusterEvalQ(cl, library(mvMonitoring))
adResults3_ls <- parLapply(cl = cl, 1:1000, function(void){
# adResults_ls <- mclapply(1:1000, mc.cores = 8L, function(void){
  ##########   Draw a Random Data Set   ##########
  adpcaObs_ls <- mspProcessData(faults = "All",
                              faultStartIndex = 8500,
                              startTime = "2016-11-27 00:00:00 CST",
                              multiState = FALSE,
                              msadpcaTest = TRUE)

@@

    ## Time to first alarm
    # Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
    # Use suppressWarnings() on the min() function. If the which() function
    # returns an integer(0), its minimum is Inf, but it throws a warning. These
    # warnings will fill the console under heavy repitition, so suppress them.
    # SPE
    time2SPE_msad <- which(msad_MS_Alarm[1000:2580,15] %in% c(2,3))
    time2SPE_msad <- suppressWarnings(min(time2SPE_msad))
    # T2
    time2T2_msad <- which(msad_MS_Alarm[1000:2580,15] %in% c(1,3))
    time2T2_msad <- suppressWarnings(min(time2T2_msad))

@@

    ## Time to first alarm
    # Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
    # SPE
    time2SPE_ad <- which(ad_MS_Alarm[1000:2580,15] %in% c(2,3))
    time2SPE_ad <- suppressWarnings(min(time2SPE_ad))
    # T2
    time2T2_ad <- which(ad_MS_Alarm[1000:2580,15] %in% c(1,3))
    time2T2_ad <- suppressWarnings(min(time2T2_ad))

@@

Let's clean up these results.
```{r adSim_Cleaning}
ss_FA_rates <- lapply(1:length(adResults_ls), function(i){
  adResults3_ls[[i]]$falseAlarmRates
}) %>% do.call(bind_rows, .)
write_csv(ss_FA_rates, path = "false_alarm_rates_ss_1000_20170320.csv")
ss_detectionTimes <- lapply(1:length(adResults_ls), function(i){
  adResults3_ls[[i]]$time2Detect
}) %>% do.call(bind_rows, .)
write_csv(ss_detectionTimes, path = "detection_times_ss_1000_20170320.csv")
```

>>>>

###  Features and State Features
We will simulate three features, with each feature operating under $k$ different states. We will use $<x(t), y(t), z(t)>$ instead of the $<x_1(t), x_2(t), x_3(t)>$ notation used in Kazor et al. This will assist us when we introduce feature states. Our state notation will be $<x_k(t), y_k(t), z_k(t)>$ for State $k$.

@@

Now we clean up the environment, and load the data we've saved.
```{r sweepEnv}
# uncomment these lines to use the data from the package. Comment them out
# when generating new data.
rm(list = ls())
data("normal_switch_xts")
data("fault1A_xts")
data("fault1B_xts")
data("fault2A_xts")
data("fault2B_xts")
data("fault3A_xts")
data("fault3B_xts")

@@

# False Alarms? 
alarmData[,ncol(alarmData)] %>% sum(na.rm = T)
alarmData[,(ncol(alarmData) - 4):ncol(alarmData)] %>% head
alarmData[,(ncol(alarmData) - 4):ncol(alarmData)] %>% tail

@@

### Import the Data files
First, we import the two data sets. 
```{r realData_import}
# # If you start working in the vignette here, then load these.
# # Otherwise, they were loaded on lines 88 and 529, respectively
# library(magrittr)
# library(tidyverse) # Includes readr
# library(mvMonitoring)
# library(xts)
if(.Platform$OS.type == "windows"){
  tenDayData_v2 <- read_csv("~/GitHub/mvMonitoring/inst/tenDayData_v2.csv", 
  col_types = cols(X1 = col_datetime(format = "%Y-%m-%d %H:%M:%S")))
currentDayData_v2 <- read_csv("~/GitHub/mvMonitoring/inst/currentDayData_v2.csv", 
  col_types = cols(X1 = col_datetime(format = "%Y-%m-%d %H:%M:%S")))
}else{
  tenDayData_v2 <- read_csv("~/Documents/GitHub/mvMonitoring/inst/tenDayData_v2.csv", 
                col_types = cols(X1 = col_datetime(format = "%Y-%m-%d %H:%M:%S")))
currentDayData_v2 <- read_csv("~/Documents/GitHub/mvMonitoring/inst/currentDayData_v2.csv",
                col_types = cols(X1 = col_datetime(format = "%Y-%m-%d %H:%M:%S")))
}

@@

### Training the AD-PCA Model
Now to analyse the training data, and pass the training information in order to test the testing data. Because the data do not come from a process with recorded state variables (or, more specifically, that we do not have such state information), we will give a column of 1s as the labels. Futher, we have ten days' worth of 10-minute-level observations, so we will train on $7 * 24 * 60 / 10 = 1008$ observations (seven days' worth), and update each day ($24 * 60 * 10 = 144$). Further, we will lag the features by one time step. CAVEAT: we're missing one observation: the `tenDay_clean` data matrix had 1299 rows, while our train (864) and returned faultChecks (434) account for 1298 rows. This missing row is the row we lost due to the lag.
```{r trainRealData}
tenDayResults_ls <- mspTrain(data = tenDay_clean,
                         labelVector = rep(1, nrow(tenDay_clean)),
                         trainObs = 1008,
                         updateFreq = 144,
                         alpha = 0.001,
                         faultsToTriggerAlarm = 3,
                         lagsIncluded = 0:1,
                         var.amnt = 0.95)
```

@@

realDataandFlags <- mspMonitor(observations = laggedOneDay,
                               labelVector = rep(1, nrow(laggedOneDay)),
                               trainingSummary = tenDayResults_ls$TrainingSpecs)
realDataandFlags[1,]
```
For some reason, that I don't know right now, `mspMonitor` is flagging all of these values as faults, which will trigger alarms for most of the day.
```{r realWarnings}
# These lines will test each line as if it was just received:
realAlarmData <- realDataandFlags
for(i in 1:nrow(realDataandFlags)){
  realAlarmData[1:i,] <- mspWarning(realAlarmData[1:i,])
}
tail(realAlarmData)
```
I'm not sure why this is happening. I'll have to dig in to it later. I do notice that both the SPE and T2 statistics are off the charts. The only component affecting them equally is the projection matrix P. We are estimating a 70 ^ 2 matrix using only 432 observations at a time, so this matrix could very well be unstable (we'd need around 2500 observations to stably estimate the scatter matrix).
EDIT: I was not supplying the training mean vector and precision matrix to the monitoring function, which means that the the test observations were not being centred and scaled. This did not make much impact in the simulated data, as the centered and scaled data would not be far off from the original values, except in state 2. This issue is fixed.

# Simulation Setup
We have also collapsed the data generation setup and implementation from this vignette into a function suite. The outward-facing function is called `mspProcessData`, and we now give an example.
```{r mspProcessEg}
# If you start working in the vignette here, then load these.
# Otherwise, they were loaded on lines 88 and 529, respectively
library(magrittr)
library(tidyverse) # Includes readr
library(mvMonitoring)
library(xts)
simFaults_ls <- mspProcessData(faults = "All",
                               faultStartIndex = 8500,
                               startTime = "2016-11-27 00:00:00 CST")

@@

## True Multi-State Observations
We first assume that the observations do come from a multi-state process. This means that we will test AD-PCA by incorrectly assuming that all observations come from the same state. We first draw a list of data matrices. Then we look at false alarm rates for multi-state data under normal operating conditions using AD-PCA and MSAD-PCA. We also measure detection time for all faults for multi-state data under normal operating conditions using AD-PCA and MSAD-PCA.
```{r trueMultiState_sim, message = FALSE}
# We get warnings of "no non-missing arguments to min; returning Inf" when
# none of the observations yield alarms. Suppress this with ? "message = FALSE"
# doesn't work.
library(parallel) # use mclapply on Mac, parLapply on Windows
a <- Sys.time()
cl <- makeCluster(getOption("cl.cores", 5))
clusterEvalQ(cl, library(tidyverse))
clusterEvalQ(cl, library(xts))
clusterEvalQ(cl, library(mvMonitoring))
msadResults5_ls <- parLapply(cl = cl, 1:5, function(void){
# msadResults2_ls <- mclapply(1:1000, mc.cores = 8L, function(void){
# msadResults5_ls <- lapply(1:1, function(void){

  ##########   Draw a Random Data Set   ##########
  msadpcaObs_ls <- mspProcessData(faults = "All",
                              faultStartIndex = 8500,
                              startTime = "2016-11-27 00:00:00 CST",
                              multiState = TRUE,
                              adpcaTest = TRUE)

@@

  # Subset out the normal operating data
  faultsSimRes <- lapply(msadpcaObs_ls[names(msadpcaObs_ls) != "NOC"],
                         function(mat){

    # Testing the apply statement
    # mat <- msadpcaObs_ls$C1

@@

    ## Time to first alarm
    alarmCol <- ncol(msad_MS_Alarm)
    # Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
    # Use suppressWarnings() on the min() function. If the which() function
    # returns an integer(0), its minimum is Inf, but it throws a warning. These
    # warnings will fill the console under heavy repitition, so suppress them.
    # SPE
    # All alarms: which(msad_MS_Alarm[1:2580,alarmCol] %in% c(2,3))
    time2SPE_msad <- which(msad_MS_Alarm[1000:2580,alarmCol] %in% c(2,3))
    time2SPE_msad <- suppressWarnings(min(time2SPE_msad))
    # T2
    # All alarms: which(msad_MS_Alarm[1:2580,alarmCol] %in% c(1,3))
    time2T2_msad <- which(msad_MS_Alarm[1000:2580,alarmCol] %in% c(1,3))
    time2T2_msad <- suppressWarnings(min(time2T2_msad))

@@

    ## Time to first alarm
    alarmCol <- ncol(ad_MS_Alarm)
    # Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
    # SPE
    # All alarms: which(ad_MS_Alarm[,alarmCol] %in% c(2,3))
    time2SPE_ad <- which(ad_MS_Alarm[1000:2580,alarmCol] %in% c(2,3))
    time2SPE_ad <- suppressWarnings(min(time2SPE_ad))
    # T2
    # All alarms: which(ad_MS_Alarm[,alarmCol] %in% c(1,3))
    time2T2_ad <- which(ad_MS_Alarm[1000:2580,alarmCol] %in% c(1,3))
    time2T2_ad <- suppressWarnings(min(time2T2_ad))

@@

  ##########   Return a List   ##########
  list(falseAlarmRates = FA_rates,
       time2Detect = faultsSimRes)
})
b <- Sys.time() 
b - a # 91 seconds for each iteration. 15.3 minutes for 10 iterations, 12.1 
# hours for 500 iterations. On parallel Mac, 5.3 minutes for 10 iterations over
# 8 cores, 41.4 minutes for 100 iterations over 8 cores, and 6.7 hours for 1000
# iterations over 8 cores. On parallel Windows, 4.3 minutes for 10 iterations
# over 8 cores, and 5.4 hours for 1000 iterations over 8 cores.
stopCluster(cl)
```
Let's clean up these results.
```{r msadSim_Cleaning}
ms_FA_rates5 <- lapply(1:length(msadResults5_ls), function(i){
  msadResults5_ls[[i]]$falseAlarmRates
}) %>% do.call(bind_rows, .)
# write_csv(ms_FA_rates4, path = "false_alarm_rates_ms_1000_20170323.csv")
ms_detectionTimes5 <- lapply(1:length(msadResults5_ls), function(i){
  msadResults5_ls[[i]]$time2Detect
}) %>% do.call(bind_rows, .)
# write_csv(ms_detectionTimes4, path = "detection_times_ms_1000_20170323.csv")
```

Now we can look at the results.
```{r msadSim_graphics}
# False Alarm Rates
ms_FA_rates5[,1] %>% hist(xlim = c(0, 0.05), main = "MSAD SPE False Alarm Rates")
ms_FA_rates5[,2] %>% hist(xlim = c(0, 0.05), main = "MSAD T2 False Alarm Rates")
ms_FA_rates5[,3] %>% hist(xlim = c(0, 0.05), main = "AD SPE False Alarm Rates")
ms_FA_rates5[,4] %>% hist(xlim = c(0, 0.05), main = "AD T2 False Alarm Rates")

###  Detection Times  ###
# Fault 1A
ms_detectionTimes5 %>%
  filter(Faults == "A1") %>%
  select(-Faults) %>% 
  sapply(summary)

# Fault 1B
ms_detectionTimes5 %>%
  filter(Faults == "B1") %>%
  select(-Faults) %>% 
  sapply(summary)

# Fault 2A
ms_detectionTimes5 %>%
  filter(Faults == "A2") %>%
  select(-Faults) %>% 
  sapply(summary)

# Fault 2B
ms_detectionTimes5 %>%
  filter(Faults == "B2") %>%
  select(-Faults) %>% 
  sapply(summary)

# Fault 3A
ms_detectionTimes5 %>%
  filter(Faults == "A3") %>%
  select(-Faults) %>% 
  sapply(summary)

# Fault 3B
ms_detectionTimes5 %>%
  filter(Faults == "B3") %>%
  select(-Faults) %>% 
  sapply(summary)

@@

## True Single-State Observations
We first assume that the observations do not come from a multi-state process. This means that we will test MSAD-PCA by incorrectly assuming that observations come from different states: we will assign a state at random to each observation from "1", "2", or "3". We first draw a list of data matrices. Then we look at false alarm rates for multi-state data under normal operating conditions using AD-PCA and MSAD-PCA. We also measure detection time for all faults for single-state data under normal operating conditions using AD-PCA and MSAD-PCA.
```{r trueSingleState_sim, message = FALSE}
# library(parallel) # use mclapply on Mac, parLapply on Windows
# library(tidyverse)
# library(xts)
a <- Sys.time()
cl <- makeCluster(getOption("cl.cores", 5))
clusterEvalQ(cl, library(tidyverse))
clusterEvalQ(cl, library(xts))
clusterEvalQ(cl, library(mvMonitoring))
adResults3_ls <- parLapply(cl = cl, 1:5, function(void){
# adResults_ls <- mclapply(1:1000, mc.cores = 8L, function(void){
  ##########   Draw a Random Data Set   ##########
  adpcaObs_ls <- mspProcessData(faults = "All",
                              faultStartIndex = 8500,
                              startTime = "2016-11-27 00:00:00 CST",
                              multiState = FALSE,
                              msadpcaTest = TRUE)

@@

    ## Time to first alarm
    alarmCol <- ncol(msad_MS_Alarm)
    # Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
    # Use suppressWarnings() on the min() function. If the which() function
    # returns an integer(0), its minimum is Inf, but it throws a warning. These
    # warnings will fill the console under heavy repitition, so suppress them.
    # SPE
    time2SPE_msad <- which(msad_MS_Alarm[1000:2580,alarmCol] %in% c(2,3))
    time2SPE_msad <- suppressWarnings(min(time2SPE_msad))
    # T2
    time2T2_msad <- which(msad_MS_Alarm[1000:2580,alarmCol] %in% c(1,3))
    time2T2_msad <- suppressWarnings(min(time2T2_msad))

@@

    ## Time to first alarm
    alarmCol <- ncol(msad_MS_Alarm)
    # Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
    # SPE
    time2SPE_ad <- which(ad_MS_Alarm[1000:2580,alarmCol] %in% c(2,3))
    time2SPE_ad <- suppressWarnings(min(time2SPE_ad))
    # T2
    time2T2_ad <- which(ad_MS_Alarm[1000:2580,alarmCol] %in% c(1,3))
    time2T2_ad <- suppressWarnings(min(time2T2_ad))

@@

Let's clean up these results.
```{r adSim_Cleaning}
ss_FA_rates <- lapply(1:length(adResults3_ls), function(i){
  adResults3_ls[[i]]$falseAlarmRates
}) %>% do.call(bind_rows, .)
# write_csv(ss_FA_rates, path = "false_alarm_rates_ss_1000_20170320.csv")
ss_detectionTimes <- lapply(1:length(adResults3_ls), function(i){
  adResults3_ls[[i]]$time2Detect
}) %>% do.call(bind_rows, .)
# write_csv(ss_detectionTimes, path = "detection_times_ss_1000_20170320.csv")
```
